Using cosmic variance to constrain the dark matter halo mass and occupation fraction of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-25 paper/ms.tex
reordering, shaping up the conclusions

\section{Additional Constraints}

@@

In this section we consider two additional constraints on the models
we accept as succesul. First we take models with the
highest possible number of mock surveys consistent with
observations. Second by comparing the angular correlation function
against observational constraints by \cite{Hayashino2004}.

@@

As an additional observational constraint we requiring that the models
selected in the previous section must be compatible with the
observational angular correlation function (ACF). The measurementens
presented in \citep{Yamada2012} do not report an ACF
measurement. Instead we use the results reported by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22.

@@

Imposing additional constraints with the maximal number of consistent
mock surveys and the angular correlation function we end up with 50
models out of the initial 90000 models. In what follows we discuss
the implications of the selection of these models on the escape
fraction of Lyman $\alpha$ radiation, the stellar abundance and the
star formation efficiency in LAEs at $z=3.1$.

\subsection{Escape fraction and allowed halo mass range}

We find that $70\%$ of the best models have a low
ocacupation fraction $f_{\rm occ}\leq 0.3$. This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
study of observational data in a wide redshift range $0<z<6$ 
\citep{Dijkstra2013}.

A complementary perspective to the range of the allowed values for the
escape fraction is the quantification of the allowed halo mass range
$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$for LAEs. In this
respect, we find that all the successful models can be  split into
three families:

@@

@@

These parameter sets can be split into three families depending the mass range
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
occupation fraction $f_{\rm occ}$. The first family is narrow both in
$\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
$\Delta M$ and the third is only narrow in $f_{\rm occ}$.

Analysis based in observations have been only able to describe models
in the third family, but have so far missed the possibility of the first
two: a narrow mass range and any value for the escape fraction.

Many different observational estimates on the occupation fraction of
LAEs at $z=3$ suggest that the occupation fraction must be low $f_{\rm
  occ}<0.2$. We find that the first and most numerous family of models
is consistent with this suggestion, where also a narrow range for the
halo mass $\Delta M<1.0$ is prefered.

>>>>

@@

In this next subsections we consider two additional constraints on the models
we accept as succesul. First we take models with the highest possible
number of mock surveys consistent with observations. Second by
comparing the angular correlation function against observational
results by \cite{Hayashino2004}.

@@

We now make a further selection to the models compatible with the
observational angular correlation function (ACF). The measurementens
presented in \citep{Yamada2012} do not report an ACF
measurement. Instead we use the results reported by
\citep{Hayashino2004} on the LAEs observed in the densest field of
SSA22.

@@

From the matching of number density statistics we find that all
the succesful models have halos in the range
$10^{10}-10^{12}$. Including strict criteria and the information from
the angular correlation function does not narrow this mass range, but
help us nevertheless to narrow down the number of good models.

matter masses of halos hosting LAEs is $\log_{10}M_{\rm
  med}=10.9^{+0.5}_{-0.9}$\Msun, with a corresponding occupation
fraction of $1-10\%$.  Our results are in a good agrement with those estimates for the
host mass. This is not unexepected given that we have also
required consistency with ACF measurements.

Together with the escape fraction $f_{\rm occ}$, quantifying the halo mass range
$\Delta M=\log_{10}M_{\rm max} - \log M_{\rm  min}$ for the succesful
models help us to classify them into three families:

@@

We find that $70\%$ of the best models have a low
occupation fraction $f_{\rm occ}\leq 0.3$.

With all the observational constraints we we end up with 50
models out of the initial 90000 combination of parameters. In what
follows we classify the resulting models into three families and
discuss them under the light of previous observational analysis from
blind galaxy surveys and other LAEs clustering analysis.

\subsection{Constraints from blind surveys}

This preference goes in
the same direction as the observational constraint on $f_{\rm occ}\sim
0.1-0.2$ derived at $z=2.2$ by \cite{Hayes2010} and recent theoretical
study of observational data in a wide redshift range $0<z<6$ 
\citep{Dijkstra2013}.

@@

These parameter sets can be split into three families depending the mass range
$\Delta M=\log_{10}M_{\rm max} - \log_{10}M_{\rm min}$ and the
occupation fraction $f_{\rm occ}$. The first family is narrow both in
$\Delta M$ and $f_{\rm occ}$, a second familiy is only narrow in
$\Delta M$ and the third is narrow in $f_{\rm occ}$ and broad in
$\Delta M$.

All the halo mass ranges in the best models fall into the broad
results based in observations, which have been able to describe models
in the third family, but have so far missed all the possible
models. In particular, previous analysis did not consider the first
two families: a narrow mass range and any value for the escape fraction.

In the case of narrow mass models there are various cases with $\Delta
M=0.1$dex. Taken at face value, a possible confirmation of these kind of models
can be considered a challenge to explain relatively high star
formation ratesm
